---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AlgalGame

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/AlgalGame)](https://CRAN.R-project.org/package=AlgalGame)
<!-- badges: end -->

The goal of AlgalGame is to solve the ODEs created by Klausmeier and Litchman (2001) and to simulate algal vertical profiles.

## Installation

You can install the released version of AlgalGame from Github with:

```{r eval = FALSE}
remotes::install_github("bishun945/AlgalGame")
```

## Example

This is a basic example which shows you how to use this pacakge.

Run the model by the default parameters:

```{r example}
library(AlgalGame)
res <- run_model()
```

Plot the result: 

```{r}
plot(res$gplot)
```


You can also plot the result by the function `ggimage` with add-on contour texts:

```{r}
ggimage(res$out, "Biomass", contour.text = TRUE)
```
The default paramters are shown as follows:

```{r}
show_parms()
```

## References

 + Klausmeier C A, Litchman E. Algal games: The vertical distribution of phytoplankton in poorly mixed water columns\[J\]. Limnology and Oceanography, 2001, 46(8): 1998-2007.
 
 + Presentation of [Algal Game](https://bishun945.github.io/presentation20201216/) in Chinese. The slide was made by [xaringan](https://github.com/yihui/xaringan).









